\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{SmartCalc v2.0}
\author{ilanadah}

\begin{document}
\maketitle

\section{Introduction}
    SmartCalc :
    \begin{itemize}
        \item The calculator has 4 operating modes: engineering calculator, loan calculator, deposit calculator, graphic calculator.
        \item The engineering calculator supports basic math operations and trigonometric functions. Expressions can contain a variable
        x”, the value of which is set after pressing “equals”.
        \item The loan calculator allows you to calculate the monthly payment, overpayment and total payment amount.
        \item The deposit calculator allows you to calculate accrued interest, tax and the amount of the deposit at the end of the term.
        \item Please note that the calculator uses a tax deduction of RUB 130 000 to calculate the tax.
    \end{itemize}

\section{Installation}

\begin{enumerate}
    \item Download the project repository;
    \item Go to the project's src folder in the terminal;
    \item Run \textbf{make install};
    \item Open the application folder on your desktop and launch the application.
\end{enumerate}

\section{Uninstalling}

\begin{enumerate}
    \item Go to the project's src folder in the terminal;
    \item Execute: \textbf{make uninstall};
    \item Delete the project folder.
\end{enumerate}

\end{document}
